Appendix to 'Detecting social information in a dense database of infants’ natural

### 2021-12-22 paper/preprint/appendix.Rmd
cleaned up activities, plotting both single-location and multi-location videos, and pr(activity|location)

```{r}
meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

meta_wide <- meta2 %>% filter(Activity!="N/A", !is.na(Location)) %>%
  select(Child, `File Name`, Activity, Location) %>%
  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',') %>%
  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',')

meta_long <- meta_wide %>% pivot_longer(cols = starts_with("Act."), 
                                        names_to = "activity_index",
                                        names_prefix = "Act.",
                                        values_to = "Activity",
                                        values_drop_na = T) %>%
  pivot_longer(cols = starts_with("Loc."),
               names_to = "location_index",
               names_prefix = "Loc.",
               values_to = "Location",
               values_drop_na = T)

@@

meta_long %>% filter(Activity!="N/A") %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Location, y=Activity, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("activity_by_location.pdf", width=6, height=10)
```

>>>>

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos.}
meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

meta_wide <- meta2 %>% filter(Activity!="N/A", !is.na(Location)) %>%
  select(Child, `File Name`, Activity, Location) %>%
  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',') %>%
  pivot_longer(cols = starts_with("Act."), 
                                        names_to = "activity_index",
                                        names_prefix = "Act.",
                                        values_to = "Activity",
                                        values_drop_na = T) %>%
  mutate(Activity = case_when(Activity=="Waving" ~ "Gesturing",
                              Activity=="Imitation" ~ "Imitating",
                              Activity=="Talking Walk" ~ "Walking",
                              Activity=="Tidying" ~ "Cleaning",
                              Activity=="Preparing for Outing" ~ "Getting Changed/Dressed",
                              Activity=="Play Pretend" ~ "Playing",
                              TRUE ~ Activity))

# include videos with multiple locations
meta_long <- meta_wide %>% 
  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',') %>%
  pivot_longer(cols = starts_with("Loc."),
               names_to = "location_index",
               names_prefix = "Loc.",
               values_to = "Location",
               values_drop_na = T)

single_locations = c("Bedroom","Car","Deck/Porch","Kitchen","Living Room","Off Property","Office","Outside on Property")

# single-location videos
meta_long_1loc <- meta_wide %>%
  filter(is.element(Location, single_locations)) %>%
  filter(Activity!="N/A", Activity!="Consequence", Activity!="Gesturing")

@@

loc_freq = sort(table(meta_long_1loc$Location))

# multi-location videos
meta_long %>% filter(Activity!="N/A", Activity!="Consequence", Activity!="Kicking",
                     Activity!="Gesturing", Activity!="Look and Listen", 
                     Location!="N/A", Location!="California Room",
                     Location!="Rapidly Moving Between Locations", Location!="Piano Room") %>%
  mutate(Location = ifelse(Location=="Dog Park/Park/Field", "Off Property", Location)) %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Activity, y=Location, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location.}
# single location videos
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Activity, y=Location, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("activity_by_location.pdf", width=6.5, height=3.5)
```

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos).}
# normalize by location
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
  group_by(Activity, Location) %>%
  summarise(n = n(),
            prop_loc = n / loc_freq) %>% 
  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
